Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Conclude

We looked at . We saw that we could modify invariants, and that doing so still provided additional
domain reduction and filtering power.

Relaxed form of the problem which is easier to solve. Far from making maximum common subgraph scale
as well as subgraph isomorphism, but we can at least get somewhere.

Future work.

>>>>

By considering a restricted variation of the problem, we have been able to go some of the way
towards tackling the maximum common subgraph problem on much larger graphs than have previously been
possible. We saw that some invariants from the subgraph isomorphism problem can still be used,
albeit in a weakened form, with considerable effect when a small number of vertices can be removed.
We have by no means cracked the problem completely---our results are still far from where we
would like them to be for use in real-world applications, and many instances remain open. However,
for many of the open instances cases we are at least able to get upper bounds on the result for the
first time.

In future work, we will combine this approach with existing lower bounding construction methods, to
deliver a hybrid algorithm. We also intend to allow restrictions on which vertices may or may not be
removed, similar to the approach of \citet{DBLP:conf/cp/ZampelliDD05}, but with much stronger
filtering now being possible.
